\textbf{Computational Fuzzy Extractors}

### 2013-02-15 CompFuzzExtUnp.tex
starting results on why unpred secure sketches are hard

\begin{lemma}
Let $X$ be the uniform distribution over $\zo^b$.  Suppose that $(\sketch, \rec)$ is a $(\zo^b, b, r, t)$ unpredictable sketch for $\epsilon = 0, s_{sec} = \Omega(|\rec|)$ with error $\delta$.  Then $r < b - t + \log (1-\delta)$.
\end{lemma}
\begin{proof}
It suffices to show that $H^{\unp}( X | \sketch(X)) < b-t + \log (1-\delta)$.  That is, it suffices to construct $D$ such that $\Pr[D(\sketch(X)) = X] > 2^{-b+t} (1-\delta)$.  We describe $D$:
\begin{enumerate}
\item Input $s = \sketch(x)$.
\item Sample $z \leftarrow \zo^b$.
\item Output $\rec(s, z)$.
\end{enumerate}
Now 
\[
\Pr[D(\sketch(X)) = X] \geq \Pr[Z \in B_t(X)] \Pr[\rec(Z, \sketch(X)) =X | \dis(Z, X)\leq t] = 2^{b-t}(1-\delta)
\]
That is $r < b-t+\log (1-\delta)$.
\end{proof}
\end{document}

>>>>

\begin{lemma}
Let $X$ be the uniform distribution over $\zo^b$.  Suppose that $(\sketch, \rec)$ is a $(\zo^b, b, r, t)$ unpredictable sketch for $\epsilon = 0, s_{sec} = \Omega(|\rec|)$ with error $\delta$.  Then $r < b - t -\log (1-\delta)$.
\end{lemma}
\begin{proof}
It suffices to show that $H^{\unp}_{0, s_{sec}}( X | \sketch(X)) < b-t + \log (1-\delta)$.  That is, it suffices to construct $D$ such that $\Pr[D(\sketch(X)) = X] > 2^{-b+t} (1-\delta)$.  We describe $D$:
\begin{enumerate}
\item Input $s = \sketch(x)$.
\item Sample $z \leftarrow \zo^b$.
\item Output $\rec(z, s)$.
\end{enumerate}
Now 
\[
\Pr[D(\sketch(X)) = X] \geq \Pr[Z \in B_t(X)] \Pr[\rec(Z, \sketch(X)) =X | \dis(Z, X)\leq t] = 2^{-b+t}(1-\delta)
\]
That is $r < b-t-\log (1-\delta)$.
\end{proof}
\bnote{Note we are underestimating the probability that $z\in B_t(x)$.  Just don't want to find the right probability right now.}
\end{document}
